Bird beak's elaboration and exploration: data preparation

### 2022-05-31 Analysis/01-Data_preparation.Rmd
Update 01-Data_preparation.Rmd

>>>>

## Passeriformes focus

```{r}
## Making a Passeriformes only list
clades_list <- as.data.frame(read.csv("../Data/Raw/BirdClades.csv", row.names = 1, stringsAsFactors = TRUE))
clades_list_passeriformes <- clades_list[which(clades_list$level2_order == "Passeriformes"), c(3, 6)]
clades_list_passeriformes[,1] <- as.factor(as.character(clades_list_passeriformes[,1]))
clades_list_passeriformes[,2] <- as.factor(as.character(clades_list_passeriformes[,2]))

## Shapespace passeriformes
shapespace_passeriformes <- shapespace[rownames(shapespace) %in% rownames(clades_list_passeriformes), ]

## Do the prep data from here (with all the trees! ouch!)
shapespace_passeriformes_suborder_family <- prep.data(
                                          level = 0, lvl.inc = c(1,2),
                                          clades    = clades_list_passeriformes,
                                          space     = shapespace_passeriformes,
                                          dim       = 1:8,
                                          consensus = consensus_tree,
                                          trees     = trees_list,
                                          verbose   = TRUE)
save(shapespace_passeriformes_suborder_family, file = "../Data/Processed/shapespace_passeriformes_suborder_family.rda")
```
